\xavier{Measuring precise radia velocities and cross-correlation function line-profile variations using a Skew Normal distribution}

### 2018-05-13 manuscript.tex
working on intro

\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
%\thanks{Based on observations collected at the La Silla Parana Observatory,
%ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}

@@

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star and also changes in the shape of the CCF. Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.

We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry. Moreover, since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.

@@

The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN. Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity. RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity. 
\comment{" interesting" is a highly subjective and not very precise or quantitative expression. Interesting in what sense? I would term this a "sentence of no value", i.e. one that conveys not useful information to the reader.}
The precision on the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN). When using the median of the SN as parameter defining the radial velocity of the star, the errors on the RVs measured by the SN are on average $10\%$ smaller than the errors calculated on the mean of the Normal.

We strongly encourage the use of the SN distribution to retrieve in 1 single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
\comment{You simply cannot make this claim. What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity. You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc. Where is the sensitivity in actually getting out useful information? Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method. I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
Grammatically this is an ambiguous statement. Are you looking for "better signals", i.e. ones that you like, or probing stellar signals in a better way? (This is what you meant, but not what was stated.)}
%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goal of RV analysis}
The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}). 
\jessi{we should mention the new spectrographs like EXPRES}
In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way. This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum. 
\comment{This is a poorly expressed thought that is technically wrong. The spectrograph does not shift due to changing atmospheric conditions (earth's atmosphere?). It changes because of mechanical shifts (vibrations, temperature changes in spectrograph housing, changes in instrumental profile) as well as movement of the image on the slit or fiber which yes, does affect stellar and iodine lines in the same way.}  
\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum. The authors show that they have no understanding how the method works. What is actually done is that a high-resolution iodine spectrum is combined with a spectrum of the star without iodine lines and a fit is made to the observed star+iodine spectrum. It is not decorrelation, but rather $\chi^2$ fitting.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar activity effect on CCF, Normal fit plus FWHM indicator}
\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.  Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}
For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}). For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
\comment{This is not true! I have taken spectra with HARPS and there is cross-talk between spectra and Th-Ar particularly for strong emission lines. So there is some contamination. Furthermore, this "preventing of contamination" as the authors state has nothing to do with the spectrograph being stablized, it has to do with the simultaneous wavelength calibration using two fibers. In fact one reference the authors give, CORALIE, is not a stabilized spectrograph!}
\comment{In paragraph 1 you give two lists of spectrographs. I presume the first one is a list spectrographs that use the iodine method, although that is not explicitly expressed. The authors talk about the iodine cell and then just give a parenthetical list of spectrographs. There is no explicit statement that these spectrographs, designed for other purposes, are all equipped with an iodine cell. The reader must assume this. Furthermore, the list is not all-inclusive. I can think of a dozen facilities that use iodine cells. So you should say, "For example" or..."to name a few"
The second list it is for simultaneous Th-Ar calibration. Not all of these are "stabilized" like the authors claim. CORALIE, if I am not mistaken, was simultaneous Th-Ar without stabilization. That is why they built HARPS. Furthermore, all of theses spectrographs were designed for precise stellar RVs, unlike the spectrographs listed for the iodine method.}

>>>>

%\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
\title{\xavier{Measuring precise radia velocities and cross-correlation function line-profile variations using a Skew Normal distribution}}
%\thanks{Based on observations collected at the La Silla Parana Observatory,
%ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}

@@

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
\xavier{Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique. Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time. Those variations are measured using the different moments of the CCF, therefore measuring with the best precision all the different moments of the CCF is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.

We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry. Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.

@@

The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN \xavier{in the case of real observations}. Therefore the CCF asymmetry and width derived using a SN are more sensitive to stellar activity, which \xavier{allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.}
\xavier{The precision on the RVs, derived using the median of the fitted SN distributions} are on average $10\%$ smaller than the RV errors calculated on the mean of the Normal. In addition, the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).

We strongly encourage the use of the SN distribution to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
\comment{You simply cannot make this claim. What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity. You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc. Where is the sensitivity in actually getting out useful information? Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method. I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
Grammatically this is an ambiguous statement. Are you looking for "better signals", i.e. ones that you like, or probing stellar signals in a better way? (This is what you meant, but not what was stated.)}
%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goal of RV analysis}

\xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}. Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs. It is therefore mandatory to understand better stellar signals and to find ways to correct for them if in the near future, we want to detect or confirm an Earth-twin planet. This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.

%for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also variations in the shape of the CCF \citep{Baranne-1996, Pepe-2002a}. As a planet induces a pure Doppler shift of its host star, the shape of the CCF should not vary with time. If it does, it is either due to instrumental systematics, or due to stellar signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2014b}. On extremely stabilized spectrographs like HARPS and HARPS-N, and soon ESPRESSO, the variations observed in the shape of the CCF or mainly due to stellar activity. Therefore, measuring with the best precision all the different moments of the CCF is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}

%The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
%\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
%You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
%This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
%\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
%For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}). 
%\jessi{we should mention the new spectrographs like EXPRES}
%In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way. This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum. 
%\comment{This is a poorly expressed thought that is technically wrong. The spectrograph does not shift due to changing atmospheric conditions (earth's atmosphere?). It changes because of mechanical shifts (vibrations, temperature changes in spectrograph housing, changes in instrumental profile) as well as movement of the image on the slit or fiber which yes, does affect stellar and iodine lines in the same way.}  
%\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum. The authors show that they have no understanding how the method works. What is actually done is that a high-resolution iodine spectrum is combined with a spectrum of the star without iodine lines and a fit is made to the observed star+iodine spectrum. It is not decorrelation, but rather $\chi^2$ fitting.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar activity effect on CCF, Normal fit plus FWHM indicator}
\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.  Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}

Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity. Stellar activity creates magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}. To differentiate between the signal induced by a planet and the one induced by stellar activity, a common technique used is tu study the different moments of the cross-correlation function (CCF). The CCF, obtained by

%For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}). For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
%\comment{This is not true! I have taken spectra with HARPS and there is cross-talk between spectra and Th-Ar particularly for strong emission lines. So there is some contamination. Furthermore, this "preventing of contamination" as the authors state has nothing to do with the spectrograph being stablized, it has to do with the simultaneous wavelength calibration using two fibers. In fact one reference the authors give, CORALIE, is not a stabilized spectrograph!}
%\comment{In paragraph 1 you give two lists of spectrographs. I presume the first one is a list spectrographs that use the iodine method, although that is not explicitly expressed. The authors talk about the iodine cell and then just give a parenthetical list of spectrographs. There is no explicit statement that these spectrographs, designed for other purposes, are all equipped with an iodine cell. The reader must assume this. Furthermore, the list is not all-inclusive. I can think of a dozen facilities that use iodine cells. So you should say, "For example" or..."to name a few"
%The second list it is for simultaneous Th-Ar calibration. Not all of these are "stabilized" like the authors claim. CORALIE, if I am not mistaken, was simultaneous Th-Ar without stabilization. That is why they built HARPS. Furthermore, all of theses spectrographs were designed for precise stellar RVs, unlike the spectrographs listed for the iodine method.}
